Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-11 paper/paper.tex
Draft of qPCR, requires a few additions, references, primer sequences

\subsection{qPCR for viral genes and IFN}

@@

\end{document}

>>>>

\subsection{qPCR for viral genes and IFN}
\abrcomment{Assuming we use the cycloheximide and ribavirin data as-is, can be modified if not}
For figures \abrcomment{whichever figures} A549 cells were seeded at a density of 10,000 cells/well in a 96-well plate in D10 media 24 hours prior to infection, with four independent wells seeded per experimental treatment. 
Immediately prior to infection D10 media was removed and replaced with influenza growth media and virus was added.
Viral infections were normalized to an MOI of a relatively pure stock of virus (0.4 for (cycloheximide figure) and 0.2 for (ribavirin figure), and identical particle numbers (calculated by qPCR, described below) of other viruses were added.
For experimental treatments of ribavirin and cycloheximde, these compounds were added to cells at the time of infection to a final concentration of 100$\mu$M and 50$\mu$g/ml, respectively.
At 8 hours post infection media was removed and cell lysates generated using the CellAmp RT-PCR for Direct Prep Kit (Real Time) \& Protein Analysis, following manufacturer's instructions. 
cDNA was synthesized using an oligoDT primer and the SuperScript III first-strand synthesis supermix from ThermoFisher using the manufacturer’s protocol. 
Transcript abundance was measured using SYBR green PCR master mix, using a combined anneal/extension step of 60 for one minute with the following primers: HA: 5’-GGCCCAACCACACATTCAAC-3’, 5’-GCTCATCACTGCTAGACGGG-3’, IFNB1: 5’-AAACTCATGAGCAGTCTGCA-3’, 5’-AGGAGATCTTCAGTTTCGGAGG-3’, L32: 5’-AGCTCCCAAAAATAGACGCAC-3’, 5’-TTCATAGCAGTAGGCACAAAGG-3’.

For titering virus by qPCR, vRNA was harvested from 80 μl of viral supernatant by the addition of 600 μl of RLT plus before proceeding with the standard QIAGEN RNeasy Plus Mini kit protocol. The cDNA was generated using SuperScript III first-strand synthesis supermix using the manufacturer’s protocol, and using the universal vRNA primers of Hoffmann et al. (add Hoffman ref) with the modifications described in Xue et al. (add Katherine ref). The qPCR was then performed as for mRNA measurements

@@

\end{document}
ent}
